Understanding Subsidy Allocation in Toronto’s Child Care Centres: Insights from a Logistic Regression Analysis

### 2024-12-11 paper/paper.qmd
updated model specification in paper

plot1

@@

- `glmnet` [@]: Applied for fitting regularized regression models and feature selection.

@@

@@

$$
\text{logit}(P(Y=1)) = \beta_0 + \beta_1 (\text{Non-Profit Auspice}) + \beta_2 (\text{CWELCC Participation}) + \beta_3 (\text{Total Space})
$$

@@

   - Measures the effect of a center being operated as a non-profit compared to the baseline (e.g., commercial auspice) on the log-odds of subsidy allocation.
   - A positive $\beta_1$ increases the likelihood of receiving a subsidy for non-profit centers relative to the reference group.

3. **$\beta_2$ (CWELCC Participation):**
   - Captures the influence of participating in the Canada-Wide Early Learning and Child Care (CWELCC) program on the log-odds of subsidy allocation.

4. **$\beta_3$ (Total Space):**
   - Represents the effect of the number of licensed child care spaces (a continuous variable) on the log-odds of subsidy allocation.

5. **$\epsilon$ (Error Term):**
   - Accounts for unexplained variation in the log-odds of subsidy allocation not captured by the predictors

>>>>

plot1
```

@@

- `glmnet` [@citeglmnet]: Applied for fitting regularized regression models and feature selection.

@@

cor_matrix <- cor(data %>% select(TOTSPACE, subsidy, cwelcc_flag), use = "complete.obs")

@@

$$
\text{logit}(P(Y=1)) = \beta_0 + \beta_1 (\text{Non-Profit Auspice}) + \beta_2 (\text{Other Auspice}) + \\ \beta_3 (\text{CWELCC Participation}) + \beta_4 (\text{Total Space})
$$

@@

- Measures the effect of a center being operated as a non-profit compared to the baseline (e.g., commercial auspice) on the log-odds of subsidy allocation.

- A positive $\beta_1$ increases the likelihood of receiving a subsidy for non-profit centers relative to commercial centers.

3. **$\beta_2$ (Other Auspice):**

- Measures the effect of a center being operated as "other type" compared to the baseline (e.g., commercial auspice) on the log-odds of subsidy allocation.

- A positive $\beta_2$ increases the likelihood of receiving a subsidy for other-type centers relative to commercial centers.

4. **$\beta_3$ (CWELCC Participation):**

- Captures the influence of participating in the Canada-Wide Early Learning and Child Care (CWELCC) program on the log-odds of subsidy allocation.

5. **$\beta_4$ (Total Space):**

- Represents the effect of the number of licensed child care spaces (a continuous variable) on the log-odds of subsidy allocation.
